---
title: "p8105_hw1_ql2370"
author: "QiLu"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

First of all, the library we used should be imported.

```{r cars, echo}
library(tidyverse)

#create a data frame
basic_df = tibble(
  random_sample = rnorm(8),
  vec_logical = random_sample > 0,
  vec_char = c("This", "is", "H", "W", "1", "done", "by", "QiLu"),
  vec_factor = factor(c("I", "I", "I", "II", "II", "II", "III", "III") )
  
)

pull(basic_df, random_sample)
pull(basic_df, vec_logical)
pull(basic_df, vec_factor)

```
The data frame is created, and means are shown by the below codes:

```{r, eval=FALSE}
mean(as.numeric(pull(basic_df,vec_logical)))
mean(as.numeric(pull(basic_df,vec_char)))
mean(as.numeric(pull(basic_df,vec_factor)))
```
Because characters have no mean, NA is shown.  
The following chunk will show more after convert every types' varible into doubles.

```{r}
# 1.convert logical vector to numberic
x = as.numeric(pull(basic_df, vec_factor))
y = x * as.numeric(pull(basic_df, random_sample))

# shows x
x
# show y
y

# 2.convert logical vertor to factor
x1 = as.factor(pull(basic_df, vec_factor))
y1 = x * as.factor(pull(basic_df, random_sample))

# shows x1
x1
# shows y1
y1

# 3.convert logical vertor to factor to numberic
x2 = as.numeric(as.factor(pull(basic_df, vec_factor)))
y2 = x2 * as.numeric(pull(basic_df, random_sample))

# shows x2
x2
# shows y2
y2


```

## Problem 2

This problem is a plot problem, so we need a seed to hold the random numbers.

```{r plot_prob2}

set.seed(1)

plot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical1 = (x + y)> 0,
  vec_numberic1 = c(as.numeric(vec_logical1)),
  vec_factor1 = c(as.factor(vec_numberic1))
)

```
The plot data frame is created. Then, I will start plot graphs by ggplot.  
The first plot will be coloring by the logical varibales, and the second will be coloring by the numberic varibles. Finally, the third one will be coloring by the factors.
```{r}
# color points using logical variables
p1 <- ggplot(plot_df, aes (x = x, y = y, color = vec_logical1)) + geom_point()
p1

# color points using numberic variables
ggplot(plot_df, aes (x = x, y = y, color = vec_numberic1)) + geom_point()

# color points using factor variables
color_factor = as.logical(as.character(pull(plot_df, vec_logical1)))
ggplot(plot_df, aes (x = x, y = y, colour = color_factor)) + geom_point()
```

The final part of problem 2 is save the first plot by ggsave. 
```{r}
# export scatterplot by ggsave
ggsave(filename = "hw1_problem2_plot", plot = p1,
    device = "pdf", path = NULL,
    scale = 1)
```

Therefore, my HW1 is finished! 
  
Thank you for grading!
  
Qi
